### 2009-11-02 doc/manuals/chelonia/arc-storage-manual.tex
arcfs is not included in final release -> commenting out fuse until solution is found

\section{Using the FUSE module} % (fold)
\label{sec:using_the_fuse_module}

Besides the \verb!chelonia! tool you can access the storage system with the use of a FUSE module. The following steps installs the ARC storage FUSE module:

\begin{itemize}
\item Install ARC1 storage system.

\item Install \verb!fuse >= 2.7.3! and \verb!fuse-python >= 0.2!:
\begin{verbatim}
$ sudo aptitude install fuse-python
\end{verbatim}

\item Make sure \verb!bartender! is set in
  \verb!$HOME/.arc/client.conf!:
\begin{verbatim}
$ grep bartender ~/.arc/client.conf 
bartender= https://chelonia1.knowarc.eu:60001/Bartender
\end{verbatim}

\item Create a mountpoint and mount arcfs:
\begin{verbatim}
   $ pwd
   /home/me/arc
   $ mkdir mnt
   $ arcfs ./mnt 
\end{verbatim}
This mounts ARCFS in \verb!/home/me/arc/mnt!, creates directory
\verb!/home/me/arc/fuse_transfer! and a log file
\verb!/home/me/arc/arcfsmessages!.

\item Make a collection:
\begin{verbatim}   
   $ mkdir -p mnt/home/me
   $ stat mnt/home/me
     File: `mnt/home/me'
     Size: 0               Blocks: 0          IO Block: 4096   directory
   Device: 19h/25d Inode: 3           Links: 2
   Access: (0755/drwxr-xr-x)  Uid: (  500/  me)   Gid: (  100/   users)
   Access: 1970-01-01 01:00:00.000000000 +0100
   Modify: 1970-01-01 01:00:00.000000000 +0100
   Change: 1970-01-01 01:00:00.000000000 +0100
\end{verbatim}
Note that so far there is no security handling implemented, so
that all files have mode 0644, all collections have mode 0755,
everything is owned by the user that mounts the system.

\item Create some entries in your collection:
\begin{verbatim}
   $ cd mnt/home/me
   $ emacs -nw fish
   catfish
   $ cat fish
   catfish
   $ cp fish fish2
   $ ls -la
   drwxr-xr-x 5 me users  0 1970-01-01 01:00 .
   drwxr-xr-x 3 me users  0 1970-01-01 01:00 ..
   -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish
   -rw-r--r-- 1 me users 28 1970-01-01 01:00 fish~
   -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish2
\end{verbatim}

\item You probably want to remove that anoying emacs backup file
\begin{verbatim}   
   $ rm fish~
   $ ls 
   fish  fish2
\end{verbatim}

\item Maybe you want fish2 in a separate collection
\begin{verbatim}   
   $ mkdir sea_creatures
   $ mv fish2 sea_creatures
\end{verbatim}

\item Maybe you're not happy with the collection name
\begin{verbatim}
   $ mv sea_creatures creatures
   $ ls creatures
   fish2
\end{verbatim}

\item Moving the collection out of ARC storage:
\begin{verbatim}
   $ cd ../../..
   $ mv mnt/home/me/creatures .
\end{verbatim}

\item The collection is no longer in the ARC storage:
\begin{verbatim}
   $ find mnt/home/me/
   mnt/home/me/
   mnt/home/me/fish
\end{verbatim}

\item Unmounting ARCFS; To unmount, refer to fuse documentation. Usually you can do
\begin{verbatim}   
   $ fusermount -u mnt
\end{verbatim}

If this for some reason this doesn't work, you can do
\begin{verbatim}   
   $ sudo umount -f mnt
\end{verbatim}

or even
\begin{verbatim}   
   $ sudo umount -l mnt
\end{verbatim}

Now, remounting the system, everything should still be there:
\begin{verbatim}
   $ arcfs ./mnt

   $ find mnt/home/me/
   mnt/home/me/
   mnt/home/me/fish

   $ fusermount -u mnt
\end{verbatim}
\end{itemize}

>>>>

%% \section{Using the FUSE module} % (fold)
%% \label{sec:using_the_fuse_module}

%% Besides the \verb!chelonia! tool you can access the storage system with the use of a FUSE module. The following steps installs the ARC storage FUSE module:

%% \begin{itemize}
%% \item Install ARC1 storage system.

%% \item Install \verb!fuse >= 2.7.3! and \verb!fuse-python >= 0.2!:
%% \begin{verbatim}
%% $ sudo aptitude install fuse-python
%% \end{verbatim}

%% \item Make sure \verb!bartender! is set in
%%   \verb!$HOME/.arc/client.conf!:
%% \begin{verbatim}
%% $ grep bartender ~/.arc/client.conf 
%% bartender= https://chelonia1.knowarc.eu:60001/Bartender
%% \end{verbatim}

%% \item Create a mountpoint and mount arcfs:
%% \begin{verbatim}
%%    $ pwd
%%    /home/me/arc
%%    $ mkdir mnt
%%    $ arcfs ./mnt 
%% \end{verbatim}
%% This mounts ARCFS in \verb!/home/me/arc/mnt!, creates directory
%% \verb!/home/me/arc/fuse_transfer! and a log file
%% \verb!/home/me/arc/arcfsmessages!.

%% \item Make a collection:
%% \begin{verbatim}   
%%    $ mkdir -p mnt/home/me
%%    $ stat mnt/home/me
%%      File: `mnt/home/me'
%%      Size: 0               Blocks: 0          IO Block: 4096   directory
%%    Device: 19h/25d Inode: 3           Links: 2
%%    Access: (0755/drwxr-xr-x)  Uid: (  500/  me)   Gid: (  100/   users)
%%    Access: 1970-01-01 01:00:00.000000000 +0100
%%    Modify: 1970-01-01 01:00:00.000000000 +0100
%%    Change: 1970-01-01 01:00:00.000000000 +0100
%% \end{verbatim}
%% Note that so far there is no security handling implemented, so
%% that all files have mode 0644, all collections have mode 0755,
%% everything is owned by the user that mounts the system.

%% \item Create some entries in your collection:
%% \begin{verbatim}
%%    $ cd mnt/home/me
%%    $ emacs -nw fish
%%    catfish
%%    $ cat fish
%%    catfish
%%    $ cp fish fish2
%%    $ ls -la
%%    drwxr-xr-x 5 me users  0 1970-01-01 01:00 .
%%    drwxr-xr-x 3 me users  0 1970-01-01 01:00 ..
%%    -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish
%%    -rw-r--r-- 1 me users 28 1970-01-01 01:00 fish~
%%    -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish2
%% \end{verbatim}

%% \item You probably want to remove that anoying emacs backup file
%% \begin{verbatim}   
%%    $ rm fish~
%%    $ ls 
%%    fish  fish2
%% \end{verbatim}

%% \item Maybe you want fish2 in a separate collection
%% \begin{verbatim}   
%%    $ mkdir sea_creatures
%%    $ mv fish2 sea_creatures
%% \end{verbatim}

%% \item Maybe you're not happy with the collection name
%% \begin{verbatim}
%%    $ mv sea_creatures creatures
%%    $ ls creatures
%%    fish2
%% \end{verbatim}

%% \item Moving the collection out of ARC storage:
%% \begin{verbatim}
%%    $ cd ../../..
%%    $ mv mnt/home/me/creatures .
%% \end{verbatim}

%% \item The collection is no longer in the ARC storage:
%% \begin{verbatim}
%%    $ find mnt/home/me/
%%    mnt/home/me/
%%    mnt/home/me/fish
%% \end{verbatim}

%% \item Unmounting ARCFS; To unmount, refer to fuse documentation. Usually you can do
%% \begin{verbatim}   
%%    $ fusermount -u mnt
%% \end{verbatim}

%% If this for some reason this doesn't work, you can do
%% \begin{verbatim}   
%%    $ sudo umount -f mnt
%% \end{verbatim}

%% or even
%% \begin{verbatim}   
%%    $ sudo umount -l mnt
%% \end{verbatim}

%% Now, remounting the system, everything should still be there:
%% \begin{verbatim}
%%    $ arcfs ./mnt

%%    $ find mnt/home/me/
%%    mnt/home/me/
%%    mnt/home/me/fish

%%    $ fusermount -u mnt
%% \end{verbatim}
%% \end{itemize}
